Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-02 paper.tex
Add content, switch to article documentclass.

\documentclass[sigconf]{acmart}

@@

\author{Edward L. Platt}
\affiliation{%
  \institution{University of Michigan}
  \city{Ann Arbor} 
  \state{Michigan} 
}
\email{elplatt@umich.edu}

@@

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{ACM proceedings, \LaTeX, text tagging}

\section{Introduction}
\epigraph
{The problem with Wikipedia is that it only works in practice. In theory, it can never work.}
{Miikka Ryokas \cite{cohen_latest_2007}}

@@

\section{Related Work}
TODO

@@

\subsection{Quantifying Performance and Efficiency}

@@

Construction

Degree

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

>>>>

% ACM
%\documentclass[sigconf]{acmart}

% Manuscript
\documentclass[10pt,twocolumn]{article}
\usepackage{natbib}

@@

% ACM
%\author{Edward L. Platt}
%\affiliation{%
%  \institution{University of Michigan}
%  \city{Ann Arbor} 
%  \state{Michigan} 
%}
%\email{elplatt@umich.edu}

% Manuscript
\author{Edward L. Platt \\ University of Michigan \\ Ann Arbor, Michigan \\ elplatt@umich.edu}

@@

% ACM
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
%\begin{CCSXML}
%\end{CCSXML}

% ACM
%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

% ACM
% \keywords{collaboration, peer production, wikipedia}

@@

\section{Introduction}
\epigraph
{The problem with Wikipedia is that it only works in practice. In theory, it can never work.}
{Miikka Ryokas \cite{cohen_latest_2007} }

@@

\section{Background and Related Work}

@@

\subsection{Efficiency and Performance}

@@

For each WikiProject, we compare the efficiency and performance measures to the structural
properties of its coeditor network.
The {\em coeditor network} of a WikiProject consists of nodes representing editors.
Two editors are connected when they have both edited the same article or talk page.
The edges are directed, with the direction representing the direction of
{\em plausible information flow};
an edge from editor A to editor B exists if A edited an article and then B edited the same article at
a later time.
Edges can exist in both directions e.g., if an article was edited first by A, then by B, and again by A.
For simplicity, we assign all edges unit weight.
We focus on three structural properties: degree, characteristic path length, and min-cut.

The node degree distribution is the simplest structural property we analyze for WikiProject
coeditor networks.
The in-degree (out-degree) of a node is the number of edges to (from) that node.
Taking the average of either in-degree or out-degree gives the same value:
the {\em mean degree} of the network.
In our context, the mean degree represents how many others a given editor has collaborated with.
We also consider the {\em skewness} of the in-degree and out-degree distributions.
A large positive degree skewness value for a WikiProject coeditor network
implies that a small number of editors have a very large number of collaborators,
while a small positive value implies that the editors having the most collaborators
don't have too many more than a typical editor.

@@

% ACM
%\bibliographystyle{ACM-Reference-Format}

% Manuscript
\bibliographystyle{acm}

\bibliography{paper}
